On The Impact of Atoms of Confusion in JavaScript Code

### 2022-07-25 0_Abstract.tex
Reviewed the abstract and intro to make thenm consistent with Sections 3 and 4.

\begin{abstract}
{\bf Context.} Engineering maintainable software is essential and must take into account \emph{how understandable the code is} from a human perspective, and spending much cognitive effort might discourage a developer when trying to familiarize herself with a legacy codebase. 
\noindent{\bf Problem.} 
%Besides lack of experience and other factors, 
Previous research works have discussed the impact of small code patterns that contribute to misunderstanding the source code written in statically typed languages (e.g., \clang, \cpplang, and Swift). However, little is known about the influence of these small code patterns (hereafter atoms of confusion) on understanding dynamically typed languages. 
\noindent{\bf Research Method and Goal.} In this work, we fill this research gap by presenting the results of a mixed-methods research:
a survey, a set of interviews with practitioners, and a mining software repositories (MSR) effort. Our goal is to investigate the impact of atoms of confusion on understanding JavaScript code---a dynamically typed language whose popularity is growing in the most different application domains (from web programming to backend and IOT development).
\noindent{\bf Results.} From our survey and interviews, we confirm that atoms of confusion lead to a code that is hard to understand: 
%removing the atoms of confusion lead to an improvement above 15\% in 6 out of 9 atoms we consider in our study when developers try to predict the outcomes of code examples. 
developers correctly predict the outcome of at least 15\% more when an atom of confusion is not present for 6 out of 9 atoms.
Also, the results of our MSR effort reveal that atoms of confusion frequently arise in open-source JavaScript systems: the \texttt{comma operator} is present in 11\% of the projects in our dataset; while five other atoms appear in more than 60\% of the projects---including the atoms \texttt{assignment as value} and \texttt{omitted curly braces}, which appear \num{8253} and \num{53357} times, respectively. Our investigation also reveals additional JavaScript constructs and idioms that might hinder developers from understanding JavaScript code. For instance, even experienced JavaScript developers agree that it is hard to understand code that uses callback functions, even though we found widespread use of \texttt{callbacks} in our projects dataset.  
\noindent{\bf Implications.} Altogether, our findings could help developers write cleaner JavaScript code and contribute to the design of new program transformation tools that aim to simplify JavaScript code. 
\end{abstract}

>>>>

\begin{abstract}
{\bf Context.} Engineering maintainable software is essential and must take into account \emph{how understandable the code is} from a human perspective, and spending much cognitive effort might discourage a developer when trying to familiarize herself with a legacy codebase. 
\noindent{\bf Problem.} 
%Besides lack of experience and other factors, 
Previous research has discussed the impact of small code patterns, called atoms of confusion, that contribute to misunderstanding the source code and for which there are functionally equivalent alternatives. These prior studies have focused on the C and Java languages. However, different languages have different features, developer communities, and development cultures. This justifies the exploration other languages to verify whether they also exhibit confusion-inducing patterns. 
\noindent{\bf Research Method and Goal.} In this work, we fill this research gap by presenting the results of a mixed-methods research: two experiments, a set of interviews with practitioners, and a mining software repositories (MSR) effort. Our goal is to investigate the impact of atoms of confusion on understanding JavaScript code---a dynamically typed language whose popularity is growing in the most different application domains (from web programming to backend and IOT development).
\noindent{\bf Results.} Both our experiments suggest that two code patterns that have been observed to confused C programmers also confuse JavaScript programmers (with statistical significance, after correction): the comma operator and assignments being used as values. In addition, 
pre- and post-increment operator, when used as values, ommitted curly braces, changes of literal encoding, and type conversions have led to confusion in at least one of the two experiments. For all these cases effect sizes were either medium or high. In addition, we have discovered the object destructuring and automatic semicolon insertion are potentially JavaScript-specific atoms that have not been discussed before. The interviews we conducted reinforce some of these findings while pointing to other constructs and idioms that merit investigation in the future.

%From our experiments and interviews, we confirm that atoms of confusion lead to code that is hard to understand. 
%removing the atoms of confusion lead to an improvement above 15\% in 6 out of 9 atoms we consider in our study when developers try to predict the outcomes of code examples. 
%developers correctly predict the outcome of at least 15\% more when an atom of confusion is not present for 9 out of 10 atoms. For 5 of these atoms, the difference is statistically significant (accounting for p-value correction) and effect size is large for 4 and medium for 1 of them. 
Also, the results of our MSR effort reveal that atoms of confusion frequently arise in open-source JavaScript systems: the \texttt{comma operator} is present in 11\% of the projects in our dataset; while five other atoms appear in more than 60\% of the projects---including the atoms \texttt{assignment as value} and \texttt{omitted curly braces}, which appear \num{8253} and \num{53357} times, respectively. Our investigation also reveals additional JavaScript constructs and idioms that might hinder developers from understanding JavaScript code. For instance, even experienced JavaScript developers agree that it is hard to understand code that uses callback functions, even though we found widespread use of \texttt{callbacks} in our projects dataset.  
\noindent{\bf Implications.} Altogether, our findings could help developers write cleaner JavaScript code and contribute to the design of new program transformation tools that aim to simplify JavaScript code. 
\end{abstract}

### 2022-07-25 main.tex
Reviewed the abstract and intro to make thenm consistent with Sections 3 and 4.

\begin{abstract}
  Evolving legacy code is a challenging task, particularly when the code has been poorly written or uses confuse idioms and language constructs, which might increase maintenance efforts and impose a significant cognitive load on developers. For this reason, researchers have investigated possible sources of confusion in codebases, including the impact of small code patterns (hereafter atoms of confusion) that contribute to misunderstanding the source code written in statically typed languages such as \clang, \cpplang, and Java. In this work, we investigate whether atoms of confusion identified in statically typed languages also confuse developers of a dynamically typed language. We use JavaScript as a representative example of dynamic programming languages and collect evidence from a mixed-method research effort: a survey, a set of interviews with practitioners, and an activity of mining open source JavaScript repositories (MSR). Our survey and interviews confirm that atoms of confusion lead to code that is hard to understand in JavaScript. Considering ten atom candidates, developers correctly predict the outcome of at least 15\% more cases in code snippets where atom candidates are not present, compared to alternative versions that include the atom candidates. For five of these atoms, the difference is statistically significant (accounting for p-value correction). Effect size is large for four atoms and medium for one of them. In addition, our MSR effort reveals that atom candidates are frequent and used intensively in 72 popular open-source JavaScript systems. Four atom candidates appear in 90\% of the analyzed projects, and two of them occur more than once for every 100 lines of code in the dataset. Altogether, our findings might help practitioners: (1) better understand the implications of atoms of confusion on understanding JavaScript code, (2) avoid writing code that is unnecessarily difficult to maintain, and (3) design program transformation tools that remove potential sources of misunderstanding in JavaScript code.
\end{abstract}

\begin{IEEEkeywords}
code readability, program comprehension, program understanding, atoms of confusion, JavaScript code
%datasets, neural networks, gaze detection, text tagging
\end{IEEEkeywords}

>>>>

\begin{abstract}
\castor{This is still too big.}
Evolving software is a challenging task, particularly when the code has been poorly written or uses confusing idioms and language constructs, which might increase maintenance effort and impose a significant cognitive load on developers. For this reason, researchers have investigated possible sources of confusion in codebases, including the impact of small code patterns (hereafter atoms of confusion) that contribute to misunderstanding the source code written in languages such as \clang, \cpplang, and Java. However, different languages have different features, developer communities, and development cultures. This justifies the exploration of other languages to verify whether they also exhibit confusion-inducing patterns. 
In this work, we fill this research gap by presenting the results of a mixed-methods research comprising two experiments, a set of interviews with practitioners, and a mining software repositories (MSR) effort. Our goal is to investigate the impact of atoms of confusion on understanding JavaScript code---a dynamically typed language whose popularity is growing in diverse application domains, e.g., web, backend, mobile, and IOT development.
Both our experiments suggest that two code patterns that have been previously observed to confuse C programmers also confuse JavaScript programmers (with statistical significance, after correction): the comma operator and assignments being used as values. In addition, pre- and post-increment operators, when used as values, omitted curly braces, changes of literal encoding, and type conversions have led to confusion in at least one of the two experiments. For all these cases effect sizes were either medium or high. In addition, we have discovered that object destructuring and automatic semicolon insertion are potential JavaScript-specific atoms that have not been discussed in previous work. The interviews we conducted reinforce some of these findings while pointing to other constructs and idioms that merit investigation in the future. In addition, our MSR effort reveals that atom candidates are frequent and used intensively in 72 popular open-source JavaScript systems. Four atom candidates appear in 90\% of the analyzed projects, and two of them occur more than once for every 100 lines of code in the dataset.
Our findings provide significant evidence that some code patterns should be avoided if code is expected to be understood by a wide audience. Furthermore, they motivate the creation of program transformation tools and the extension of linters to address these potentially harmful idioms in JavaScript codebases.
\end{abstract}

%\begin{IEEEkeywords}
%code readability, program comprehension, program understanding, atoms of confusion, JavaScript code
%datasets, neural networks, gaze detection, text tagging
%\end{IEEEkeywords}
